%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Alex Eum} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 917-913-9466 ~ \href{mailto:alexhyuneum@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{alexhyuneum@gmail.com}} ~ 
    \href{https://linkedin.com/in/alexander-eum/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/alexander-eum}}  ~
    \href{https://github.com/alexeum31}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/alexeum31}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Princeton University}{Sep. 2022 -- May 2026}
      {Bachelor of Arts in Computer Science}{Princeton, NJ}
      \begin{itemize}[itemsep=-5pt, parsep=5pt]
                \item\small Awards: Magna Cum Laude, Sigma Xi Research Honors Society, 2nd/80 at Princeton Poker Tournament
                \item\small GPA: 3.7/4.0
                
            \end{itemize}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
    % %\resumeSubHeadingListStart
    %     \begin{multicols}{3}
    %         \begin{itemize}[itemsep=-5pt, parsep=5pt]
    %             \item Distributed Systems (TA)
    %             \item Operating Systems (TA)
    %             \item\small Data Structures \& Algorithms (TA)
    %             \item Programming Systems (TA)
    %             \item Moments of Computing (Graduate)
    %             \item Computer Networks (TBD)
    %             \item Computer Architecture 
    %             \item Functional Programming 
    %             \item Advanced Program Techniques
    %             \item Discrete Math
    %             \item Machine Learning
    %             \item Linear Algebra
    %         \end{itemize}
    %     \end{multicols}
    %     \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Optiver}{Aug. 2026}
      {Software Engineer}{New York City, NY}

       
    \resumeSubheading
      {IMC Trading}{Jun. 2025 -- Aug. 2025}
      {Software Engineer Intern}{Chicago, IL}
      \resumeItemListStart
      \resumeItem{Developing CME exposure-based quote grouping system using \textbf{C++23}, enabling rapid quote cancellation to prevent adverse selection during simultaneous shifts in theoretical values of thousands of US Treasuries and commodities options}
      \resumeItem{Conducted component and end-to-end dev tests that ensured correctness within a simulated production environment}
      \resumeItem{Presented the project’s impact and provided background on options theory to leaders across the execution organization}
       \resumeItemListEnd


    
    \resumeSubheading
      {Meta}{May 2024 -- Aug. 2024}
      {Software Engineer Intern}{Menlo Park, California}
      \resumeItemListStart
        \resumeItem{Constructed ML holdout infrastructure from scratch using \textbf{Hack/PHP}, achieving a \textbf{54\%} reduction in False Discovery Rate across all scam detection models, with robust extensibility to support models from external organizations}
        \resumeItem{Analyzed \textbf{XGBoost} models through \textbf{Python dataswarm} pipelines that streamlined logging into Hive tables. Ran \textbf{SQL} queries to track FDR changes across several scam detection models and displayed findings on a dashboard}
      \resumeItemListEnd

    \resumeSubheading
      {LG U+}{Jun. 2023 -- Aug. 2023}
      {Software Engineer Intern}{Yongsan-Gu, Seoul}
      \resumeItemListStart
        \resumeItem{Utilized \textbf{Google Analytics} to identify pain points, increasing \textbf{user flow by 34\%} by pinpointing key user-facing bugs}
        \resumeItem{Optimized backend API performance, reducing response times by \textbf{17\%} through targeted endpoint/test refactoring}
      \resumeItemListEnd

    \resumeSubheading
      {Cubits.AI}{May 2023 -- Jun. 2023}
      {Software Engineer Intern}{Virtual}
      \resumeItemListStart
        \resumeItem{Developed a chat-driven mobile application using \textbf{ReactJS} from scratch to sell reverse-classroom style college courses}
        \resumeItem{Engineered prompts to query \textbf{OpenAI API} Platform, created a chatbot that summarizes videos and creates quizzes}
      \resumeItemListEnd

    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{IOCL on Chain Replication with Apportioned Queries} $|$ \emph{C++}}{Sep. 2025 -- May 2026}
          \resumeItemListStart
	    \resumeItem{Formalized IOCL, a consistency model with cross-shard \textbf{invocation-order} guarantees for \textbf{concurrent} clients}
	    \resumeItem{Designed and implemented protocol in \textbf{C++} and benchmarked against CRAQ to reduce \textbf{WAN latency} by \textbf{72\%}}
          \resumeItemListEnd 
          \vspace{-13pt}

    \vspace{-5pt}
        \resumeProjectHeading
          {\textbf{Optimizing the BBR Algorithm for Video Streaming} $|$ \emph{C, Mininet}}{Jan. 2025 -- Apr. 2025}
          \resumeItemListStart
            \resumeItem{\textbf{Authored research paper} enhancing \textbf{BBR-S} TCP congestion control by optimizing bottleneck bandwidth estimation}
            \resumeItem{Determined optimal $hist\_percentile$ interval \textbf{(85, 95]}, reducing bufferbloat and RTT while maintaining high goodput}
          \resumeItemListEnd 
          \vspace{-13pt}

          
           \resumeProjectHeading
          {\textbf{C-to-PDP-11 Compiler and Assembler} $|$ \emph{LLVM, Python, C/C++, Assembly}}{Mar. 2025 -- Apr. 2025}
          \resumeItemListStart
            \resumeItem{Developed a pipeline to compile C code PDP-11 assembly code by utilizing \textbf{Clang} (LLVM) and \textbf{Python llvmlite}}
            \resumeItem{Utilized \textbf{macro11} to implement an assembler that converts \textbf{PDP-11 assembly} code to machine code and emulated it}
          \resumeItemListEnd 
          \vspace{-13pt}
          
          \resumeProjectHeading
          {\textbf{Xv6 Operating System} $|$ \emph{C}}{Jan. 2025 -- Apr. 2025}
          \resumeItemListStart
            \resumeItem{Developed OS that implements \textbf{virtual memory} with file-backed, shared mappings, a \textbf{stride scheduler} that uses dynamic process participation to fairly schedule processes, and system calls to \textbf{spawn} and \textbf{destroy threads}}
          \resumeItemListEnd 
          \vspace{-13pt}

          
          \resumeProjectHeading
          {\textbf{Raft Consensus Algorithm} $|$ \emph{Go}}{Jan. 2025 -- Mar. 2025}
          \resumeItemListStart
            \resumeItem{Developed Raft’s \textbf{distributed consensus} algorithm, providing fault tolerant leader election and log replication that achieves strict consistency (\textbf{linearizability}) and ensures strong correctness guarantees under \textbf{concurrency}}
          \resumeItemListEnd 
          \vspace{-13pt}
          
          
          \resumeProjectHeading
          {\textbf{Moogle Web Crawler} $|$ \emph{OCaml}}{Oct. 2024 -- Nov. 2024}
          \resumeItemListStart
            \resumeItem{Engineered a Scalable Web Crawler to build an index mapping words to web pages using recursive link exploration}
            \resumeItem{Developed a \textbf{PageRank}-inspired algorithm leveraging link-based propagation to calculate importance scores}
            \resumeItemListEnd 
          \vspace{-13pt}
          
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, C, Python, Java, Golang, OCaml, Bash, SQL, Hack, PHP, HTML/CSS, JavaScript, JSX, Assembly, Latex} \\
     \textbf{Developer Tools}{: Linux, nvim, i3wm, tmux, Git, MongoDB, PostgreSQL, Qt, Google Analytics, AJAX, VS Code} \\
    }} 
 \end{itemize}
 \vspace{-16pt}



\end{document}

% test trigger
% test trigger
